---
output: 
    github_document:
        html_preview: false
---
# `Dipol2Red`

`Dipol2Red` is a package for reducing data obtained with a double-imaging polarimeter *Dipol-2* (and any later versions of *Dipol* family polarimeters).

The input data are the differences (in magnitudes) between ordinary and extraordinary rays of a given target on the image and respective timestamps (or any other sortable numeric identifier). The data are generated as a result of subsequent observations with different phase plate angle (22.5 deg step). Every 16 measurement correspond to one full plate rotation, every 4 measurements produce one (independent polarization measurement).

Such stream of `4n` data is transformed into polarization measurement. If no grouping is provided, all data are used to compute one average (over the whole data set).
Alternatively, data can be grouped by `4m` subsequent observations (using `dplyr::group_by`), and the averaging procedure is applied to each group separately, providing the best control.

## Example usage
```{r}
library(tibble, quietly = TRUE, warn.conflicts = FALSE)
library(dplyr, quietly = TRUE, warn.conflicts = FALSE)
library(Dipol2Red, quietly = TRUE, warn.conflicts = FALSE)
```

- Simulating one observation with `1 %` polarization in `x` direction.
4 measurements corresponding to plate angles 0, 22.5, 45, 67.5 deg.
    ```{r}
    x_1 <- tibble(
        JD = c(1, 2, 3, 4), 
        Obs = 2.5 * log10(c(102, 100, 98, 100)))
    fsigma_2(x_1)
    ```

- Simulating total polarization of `1 %` and equal `x` and `y` components.
    ```{r}
    x_2 <- tibble(
        JD = 10 + c(1, 2, 3, 4), 
        Obs = 2.5 * log10(c(101.4142, 101.4142, 98.5858, 98.5858)))
    fsigma_2(x_2)
    ```

- Combining two datasets to obtain average over several observations.
    ```{r}
    x_3 <- bind_rows(x_1, x_2)
    fsigma_2(x_3)
    ```

- Assigning groups, separating observations by `Run`. Recreates two original measurements. `fsigma_2` automatically detects grouping variables and appends these values to the output.

    ```{r}
    x_4 <- mutate(x_3, Run = factor(if_else(JD < 10, "First", "Second")))
    x_4 <- group_by(x_4, Run)
    fsigma_2(x_4)
    ```